\documentclass[conference, final]{IEEEtran}
%\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{comment}
\usepackage{booktabs}

\usepackage[bordercolor=gray!20,backgroundcolor=red!10,linecolor=red!50,textsize=scriptsize,textwidth=0.51in,obeyFinal]{todonotes}
\setlength{\marginparwidth}{0.51in}
\setlength{\marginparsep}{0.10in}
\usepackage{soul}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\bibliographystyle{ieeetr}

% ======================================
% trying to save space
\usepackage[compact]{titlesec}
\titlespacing{\section}{0pt}{0pt}{0pt}
\AtBeginDocument{
  \setlength\abovedisplayskip{0pt}
  \setlength\belowdisplayskip{0pt}}
\setlength{\textfloatsep}{2pt plus 0pt minus 0pt}
\setlength{\floatsep}{2pt plus 0pt minus 0pt}
\setlength{\intextsep}{2pt plus 0pt minus 0pt}
% ======================================  

%\renewcommand{\textcolor}[2]{#2}
\newcommand{\red}[1]{\textcolor{red}{#1}}
\newcommand{\green}[1]{\textcolor{green}{#1}}
\newcommand{\az}[1]{\todo[backgroundcolor=blue!10,linecolor=blue!50]{\textbf{Zaher:} #1}}


\begin{document}
\setstcolor{blue}
\title{Drones with Networking and Machine Learning for Smart City Applications: A Review\\
%{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
%should not be used}
\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{Masud Ahmed\textsuperscript{*}, Naima Khan, Abu Zaher Md Faridee, Nirmalya Roy}
\IEEEauthorblockA{\textit{dept. Information Systems} \\
\textit{University of Maryland Baltimore County}\\
Baltimore, USA \\
%*mahmed10@umbc.edu
}
}

\maketitle

\begin{abstract}
Unmanned Aerial Vehicle\textcolor{red}{s}, alternatively known as drone\textcolor{red}{s}, operate without any pilot on board. Starting with
surveillance, disaster management, infrastructure monitoring, drones provide unparalleled opportunities to improve our daily life with large scale IoT (Internet of thing\textcolor{blue}{s}) based applications. Nonetheless, the drone systems are facing significant limitations \textcolor{red}{in a number of areas, such as} autonomous operation, \textcolor{red}{sustaining} longer flight duration, large\textcolor{red}{-scale} data collection,
% on a single platform, 
obstacle avoidance, reliable real-time application \textcolor{red}{etc.} In this review paper, we first summarize a few research works that have proposed solutions to these constraints. We then discuss recent machine learning-based drone applications that can increase our working efficiency in numerous sectors. After that, we analyze different communication protocols and sensors that are being used with drones. We also present several drone-based challenges and datasets that may help the upcoming researchers in this field. Finally, we conclude our review by discussing the applications of drones in the current COVID-19 situation and the effects of the pandemic on the overall drone industry.

\end{abstract}

\begin{IEEEkeywords}
UAV, ummanned aerial vehicle, drone, inspection, tracking, autonomous navigation, safe landing, disaster management, supply chain, COVID-19.
\end{IEEEkeywords}

\input{section/intro}
\input{section/networking}
%\input{section/signalprocessing}
\input{section/application}
\input{section/dataset}
\input{section/toolkit}
\input{section/covid19}
\input{section/challenge}
\input{section/conclusion}

%\subsection{Networking}

%\subsection{Computer Vision}
%Object Tracking, Data Augmentation

%\subsection{Hardware platform}
%something related to mechanical
\bibliography{sample}

\end{document}